A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-12-10 paper/MSDS7330DBMSforGeospatiallyEnabledGame.tex
Vlad's changes to the paper
Minor errors

\begin{figure}
\centering
\includegraphics[width=2.5in]{imgs/UserInterface.png}
\caption{Diagram of User and Server Interfaces}
\label{UserInterface}
\end{figure}
Pictorial description above:

@@

Our application is not eligible for Apple Store since Apple does not allow prototypes to be shared with public. We use Apple’s TestFlight instead to share our game with anyone who wants to try it. To get our game on your device make sure your iPhone is 7 or higher and your iOS is updated to at least version 12.0.  Next, follow this link from your device to install Apple's TestFlight and our game:

@@

\begin{center}
\textit{\small{\url{https://www.youtube.com/watch?v=ISu8_D99u3o}}}. 
\end{center}

>>>>

\begin{figure}
\centering
\includegraphics[width=2.5in]{imgs/UserInterface.png}
\caption{Diagram of User and Server Interfaces}
\label{UserInterface}
\end{figure}

@@

Our application is not eligible for Apple Store since Apple does not allow prototypes to be shared with public. We use Apple’s TestFlight instead to share our game with anyone who wants to try it. To get our game on your device make sure your iPhone is 6s (model A1688) or higher and your iOS is updated to at least version 12.0.  Next, follow this link from your device to install Apple's TestFlight and our game:

@@

\begin{center}
\textit{\small{\url{https://goo.gl/xrNPXQ}}}. 
\end{center}
